Approximating Information-Theoretic Scores\\for Computer Adaptive Tests\\in Bayesian and Credal Networks

### 2021-04-18 paper.tex
First change

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{xcolor} 
\usepackage{amsmath} 
\usepackage{amstext} 
\usepackage{amssymb} 
\usepackage{amsfonts} 
\usepackage{mathptmx} 
\usepackage[scaled=.90]{helvet} 
\usepackage{courier} 
\usepackage{textcomp} 
\usepackage{hyperref} 
\usepackage{array}
\usepackage{varwidth}
\usepackage[american]{babel}
\usepackage{mathtools} % fixes and extends amsmath
\mathtoolsset{mathic}
\allowdisplaybreaks
\usepackage{mathptmx}
\usepackage{tabu}
%\usepackage{breqn}
\usepackage{algorithm,algorithmic,bm}
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
\renewcommand\UrlFont{\color{blue}\rmfamily}
%% Suggested packages, as needed:
\usepackage{booktabs} % commands to create good-looking tables
\usepackage{tikz} % nice language for creating drawings and diagrams - required for 
%drawing custom shapes
\usetikzlibrary{%
	arrows,%
	calc,%
	fit,%
	patterns,%
	plotmarks,%
	shapes.geometric,%
	shapes.misc,%
	shapes.symbols,%
	shapes.arrows,%
	shapes.callouts,%
	% shapes.multipart,%
	% shapes.gates.logic.US,%
	% shapes.gates.logic.IEC,%
	% er,%
	% automata,%
	backgrounds,%
	chains,%
	topaths,%
	trees,%
	petri,%
	mindmap,%
	matrix,%
	% calendar,%
	folding,%
	fadings,%
	through,%
	positioning,%
	scopes,%
	decorations.fractals,%
	decorations.shapes,%
	decorations.text,%
	decorations.pathmorphing,%
	decorations.pathreplacing,%
	decorations.footprints,%
	decorations.markings,%
	shadows}
\usetikzlibrary{arrows,automata,circuits}
\usepackage{pgfplots}
\pgfplotsset{compat=1.13}
\usepackage{pgfkeys}
%\usepackage{trace-pgfkeys}
\begin{document}
\title{Approximating Information-Theoretic Scores\\for Adaptive Tests}
%%\thanks{Supported by organization x.}}
%\titlerunning{Abbreviated paper title}
\author{permutation of Alessandro Antonucci \and
Francesca Mangili \and
Claudio Bonesana\and
Giorgia Adorni}
\authorrunning{F. Author et al.}
\institute{Dalle Molle Institute for Artificial Intelligence USI-SUPSI -- IDSIA \\
\email{\{alessandro,francesca,claudio.bonesana,giorgia.adorni\}@idsia.ch}}
\maketitle          
\begin{abstract}
A test is adaptive when the sequence and the number of questions is tuned on the basis of the estimated skill levels of the test taker. Graphical models such as Bayesian networks allow to model the uncertainty about the questions and the skills in an highly interpretable fashion, especially when coping with multiple skills. Yet, the quantification of the uncertainty in the question/skill relations can be better quantified by interval-valued probabilistic values in the model. This might make inference considerably harded in the underlying model, this being especially the case for the information theoretic quantity generally used for these models. We present.

with xxx. Interval valued quantification

We suggest the use of credal networks, a generalization of Bayesian networks based on sets of probability mass functions, to implement adaptive tests exploiting the knowledge of the test developer instead of training on databases of answers. Compared to Bayesian networks, these models might offer higher expressiveness and hence a more reliable modeling of the qualitative expert knowledge. The counterpart is a less straightforward identification of the 
information-theoretic measure controlling the question-selection and the test-stopping criteria. We elaborate on these issues and propose a sound and computationally feasible procedure. Validation against a Bayesian-network approach 
on a benchmark about German language proficiency assessments suggests that credal networks can be reliable in assessing the student level and  effective in reducing the number of questions required to do it.
%\keywords{credal networks  \and adaptive test \and bayesian network.}
\end{abstract}
\section{Testing Algorithms}
The typical goal of a test or exam is to evaluate the knowledge level of a student or examinee $\sigma$ on the basis of her answers to a number of questions or exercises. Let $\bm{Q}$ denote a repository of questions available to the instructor. The order and the number of questions from $\bm{Q}$ asked to $\sigma$ might not be fixed. We call \emph{testing algorithm} (TA) a procedure taking care of the selection of the sequence of questions asked to the student and able to decide when the test should stop. A standard TA pseudocode is in Algorithm \ref{alg:ta}, where $\bm{e}$ denotes the array of the answers collected from the student $\sigma$.

\begin{algorithm}[htbp!]
    \caption{Testing algorithm. Student profile $\sigma$ and question repository $\bm{Q}$ are inputs.}
    \begin{algorithmic}[1]
    \STATE $\bm{e}=\emptyset$
        \WHILE{ {\bf not} $\tt{Stopping}(\bm{e})$}
        \STATE $Q^* \gets \tt{PickQuestion}(\bm{Q},\bm{e})$
        \STATE $q^* \gets {\tt{Answer}}(Q^*,\sigma)$
        \STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
        \STATE $\bm{Q} \gets \bm{Q} \setminus \{ Q^*\}$
        \ENDWHILE
        \STATE {\bf return} $\tt{Evaluate}(\bm{e})$
    \end{algorithmic}\label{alg:ta}
\end{algorithm}

@@

	\begin{algorithm}[htp!]
		\caption{Single skill, precise model\\
			a model (BN, skeleton) $M$ over the skills only
			\\a dataset of $n$ students $\{s^i\}_{i=1}^n$,\\a dataset of $m$ questions 
			$\mathcal{Q}:=\{Q^j\}_{j=1}^m$,\\
			the CPTs of the questions in $\mathcal{Q}$, i.e., $\{P(Q^j|S)\}_{j=1}^m$\\
			the student answer models $\{\tilde{P}(Q^j|S)\}$\\
			an entropy threshold $h^*$,\\
			a score function for questions $\gamma$
			\label{alg:simple}}
		\begin{algorithmic}[1]
			\FOR {$i\gets\{1,\ldots,n\}$}
			\STATE $(M',\mathcal{Q}',\mathcal{Q}'',\bm{e}) \gets 
			(M,\mathcal{Q},\emptyset,\emptyset)$
			\WHILE{ $h > h^* \mathrm{\bf and}\, \mathcal{Q}' \neq \mathcal{Q}$}
			\STATE $Q^* \gets \arg\max_{Q \in \mathcal{Q}'}\gamma(M',Q,\bm{e})$
			\STATE{$\mathcal{Q}'\gets \mathcal{Q}' \setminus \{ Q^*\}$}
			\STATE{$\mathcal{Q}''\gets \mathcal{Q}'' \cup \{ Q^*\}$}
			\STATE{$q^* \gets \mathrm{sampling} \sim \tilde{P}(Q^*|s^i)$}
			\STATE $M' \gets \mathrm{addChild}(M',Q,S,P(Q|S))$
			\STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
			\STATE $h \gets H[P_{M'}(S|\bm{e})]$
			\ENDWHILE
			\STATE $\sigma_i \gets \arg\max_{s\in\mathcal{S}} P_{M'}(s|\bm{e})$
			\ENDFOR
			\STATE {\bf return} $(\sigma_1,\ldots,\sigma_n)$
		\end{algorithmic}
	\end{algorithm}
	Three possible scores:
	\begin{eqnarray}
		\gamma(Q,\bm{e}) := -H[S|Q,\bm{e}] = -\sum_q P(q) \cdot H[S|\bm{e},q]&&\\
		\gamma'(Q,\bm{e}) :=  -\sum_q P(q) \cdot \max_{s\in\mathcal{S}}  P[s|\bm{e},q]&&\\
		\gamma''(Q,\bm{e}) :=  |P(Q=1|\bm{e})-0.5|&&
	\end{eqnarray}

@@

	\begin{algorithm}[htp!]
		\caption{Single skill, credal model\\a dataset of $n$ students $\{s^i\}_{i=1}^n$,\\a 
		dataset of $m$ questions $\mathcal{Q}:=\{Q^j\}_{j=1}^m$,\\
			the credal CPTs of the questions in $\mathcal{Q}$, i.e., 
			$\{\overline{P}(Q^j|S)\}_{j=1}^m$\\
			an upper entropy threshold $\overline{h}^*$,\\
			a score function for questions $\sigma$
			\label{alg:simple2}}
		\begin{algorithmic}[1]
			\FOR {$i\gets\{1,\ldots,n\}$}
			\STATE $(\mathcal{Q}',\mathcal{Q}'',\bm{e}) \gets 
			(\mathcal{Q},\emptyset,\emptyset)$
			\WHILE{ $h > h^* \mathrm{\bf and}\, \mathcal{Q}' \neq \mathcal{Q}$}
			\STATE $Q^* \gets \arg\max_{Q \in \mathcal{Q}'}\gamma(Q,\bm{e})$
			\STATE{$\mathcal{Q}'\gets \mathcal{Q}' \setminus \{ Q^*\}$}
			\STATE{$\mathcal{Q}''\gets \mathcal{Q}'' \cup \{ Q^*\}$}
			\STATE{$q^* \gets \mathrm{sampling} \sim P(Q^*|s^i)$}
			\STATE $\mathrm{addChild}(Q,S,P(Q|S))$
			\STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
			\STATE $h \gets H[P(S|\bm{e})]$
			\ENDWHILE
			\STATE $\sigma_i \gets \arg\max_{s\in\mathcal{S}} P(s|\bm{e})$
			\ENDFOR
			\STATE {\bf return} $(\sigma_1,\ldots,\sigma_n)$
		\end{algorithmic}
	\end{algorithm}
	Three possible scores:
	\begin{eqnarray}
		\gamma(Q,\bm{e}) := -H[S|Q,\bm{e}] = -\sum_q P(q) \cdot H[S|\bm{e},q]&&\\
		\gamma'(Q,\bm{e}) :=  -\sum_q P(q) \cdot \max_{s\in\mathcal{S}}  P[s|\bm{e},q]&&\\
		\gamma''(Q,\bm{e}) :=  |P(Q=1|\bm{e})-0.5|&&
	\end{eqnarray}

	\begin{algorithm}[htp!]
		\caption{Given a dataset of student profiles $\bm{S}$\label{alg:simple3}}
		\begin{algorithmic}[1]
			\FOR {$s\in\bm{S}$}
			\WHILE{ $h > h^*$}
			\STATE $Q^* \gets \mathrm{FindBestQuestion}(\bm{Q}$)
			\STATE $q^* \gets \mathrm{SimulateAnswer}(\sigma)$
			\STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
			\STATE $h \gets H[P(S|\bm{e}]$
			\ENDWHILE
			\ENDFOR
			\STATE {\bf return} $\arg\max P(s|\bm{e})$
		\end{algorithmic}
	\end{algorithm}

@@

	\subsection*{Toy Example}
	Consider a Boolean skill $S$ with states $s_0$ and $s_1$ and a Boolean 
	question/answer $Q$. Let us shape the model as a BN, $S\to Q$. The prior $P(S)$ is 
	specified by a parameter $p:=P(s_1)$. The question CPT $P(Q|S)$ might be specified 
	instead by two parameters $\pi_1:=P(q_1|s_1)$ and $\pi_0:=P(q_1|s_0)$. The 
	informativeness score we assign two the question is
	\begin{equation}
		\sigma_Q = H[S|Q]:=H[S|q_0]P(q_0)+H[S|q_1]P(q_1)\,.
	\end{equation}
	We have
	\begin{equation}
		P(q_1)=\pi_1 p + \pi_0 (1-p)
	\end{equation}
	while $P(q_0)=1-P(q_1)$ and also
	\begin{equation}
		P(s_1|q_1)=\frac{\pi_1 p}{\pi_1 p + \pi_0 (1-p)}=\frac{1}{1+\frac{\pi_0(1-p)}{\pi_1 p}}
	\end{equation}
	and
	\begin{equation}
		P(s_1|q_0)=\frac{p (1-\pi_1)}{p(1-\pi_1) +  (1-p)(1-\pi_0)} = \frac{1}{1+ \frac{ 
		(1-p)(1-\pi_0)}{p (1-\pi_1)}} 
	\end{equation}
	while $P(S=0|Q=1)$ by normalization. Accordingly:
	\begin{multline}
		\sigma_Q(p,\pi_0,\pi_1)=\\
		h \circ f[\gamma/l(p)] \cdot t +
		h \circ f[\gamma'/l(p)] \cdot (1-t)\,
		%\theta(\frac{\pi_0(1-p)}{\pi_1 p}) [\pi_1 p + \pi_0 (1-p)]\\
		%+ \theta(\frac{ (1-p)(1-\pi_0)}{p (1-\pi_1)}) [1-\pi_1 p + \pi_0 (1-p)]
	\end{multline}
	where $\gamma = \frac{\pi_0}{\pi_1}$, $\gamma' = \frac{1-\pi_0}{1-\pi_1}$, and $t = \pi_1 
	p + \pi_0 (1-p)$.

@@

	\begin{multline}
		\sigma_Q(p,\pi_0,\pi_1)=\\
		m\bigl(\frac{\pi_1 p}{P(q_1)}\bigr) \cdot P(q_1)  +
		m\bigl(\frac{(1-\pi_1) p}{1-P(q_1)}\bigr) \cdot (1-P(q_1))\,
	\end{multline}

	But, as $P(q_1)\geq 0$, then
	\begin{multline}
		m\bigl(\frac{\pi_1 p}{P(q_1)}\bigr) =\\
		2max\bigl(\frac{\pi_1 p}{P(q_1)},1-\frac{\pi_1 p}{P(q_1)} \bigr) =\\
		2max\bigl(\frac{\pi_1 p}{P(q_1)},\frac{\pi_0(1- p)}{P(q_1)} \bigr) =\\
		\frac{2}{P(q_1)}max\bigl(\pi_1 p,\pi_0(1- p)\bigr).\\
	\end{multline}

	Similarly, as $1-P(q_1)\geq 0$, 
	\begin{multline}
		m\bigl(\frac{(1-\pi_1) p}{1-P(q_1)}\bigr) =\\
		\frac{2}{1-P(q_1)}max\bigl((1-\pi_1) p,(1-\pi_0)(1- p)\bigr),\\
	\end{multline}

@@

	\begin{multline}
		\sigma_Q(p,\pi_0,\pi_1)= \\
		2 max\{\pi_1 p, \pi_0 (1-p)\}+
		2 max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\}\,
	\end{multline}

@@

	However I think we can split the optimization into 4 quadratic optimizations.
	Let's use the following parametrization:
	\begin{multline}\label{eq:minimization}
		\min_{p,\pi_0,\pi_1} \sigma_Q(p,\pi_0,\pi_1) = \\
		2\min_{p,\pi_0,\pi_1} \bigl( \max\{\pi_1 p, \pi_0 (1-p)\} + \\
		~~~ \max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\} \bigr) \approx \\
		2 \bigl( \min_{p,\pi_0,\pi_1}  \max\{\pi_1 p, \pi_0 (1-p)\} + \\
		~~~ \min_{p,\pi_0,\pi_1} \max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\} \bigr) 
	\end{multline}

@@

	\begin{multline}
		\tilde{P}(s=0,q) = \min_{\pi_1 ,p} \pi_1 p \\
		\begin{array}{ll}
			\text{subject to} & \pi_1 p > \pi_0 (1-p) \\
			~&\underline{x} \leq x\leq \overline{x}\\ 
		\end{array}
	\end{multline}
	and 
	\begin{multline}
		\tilde{P}(s=1,q) = \min_{\pi_0 ,p} \pi_0 (1-p) \\
		\begin{array}{ll}
			\text{subject to} & \pi_1 p < \pi_0 (1-p)\\
			~&\underline{x} \leq x\leq \overline{x}\\ 
		\end{array}
	\end{multline}

@@

	\begin{multline}
		\tilde{P}_1 = \min_{\pi_0,\pi_1,p} \pi_1 p+ (1-\pi_1)p = p \\
		\begin{array}{ll}
			\text{subject to} & \pi_1 p > \pi_0 (1-p) \\
			~&  (1-\pi_1)p > (1-\pi_0)(1-p)  \\
			~&\underline{x} \leq x\leq \overline{x}\\ 
		\end{array}
	\end{multline}
	and so on. However, in this case, the number of optimizations to solve should be 
	$N_s^{N_q}$, that is, it grows exponentially with  $N_q$.

>>>>

\documentclass[runningheads]{llncs}
\usepackage[]{algorithm2e}
\usepackage[]{algorithmic}
\usepackage{bm,hyperref,booktabs,tikz,pgf,pgfplots,amsmath}
\usetikzlibrary{arrows,automata,circuits}
%\pgfplotsset{compat=1.13}
%\usepackage{pgfkeys}
%\usepackage{graphicx}
%xcolor} 
%amsmath} 
%amstext} 
%amssymb} 
%amsfonts} 
%\usepackage{mathptmx} 
%\usepackage[scaled=.90]{helvet} 
%\usepackage{courier} 
%\usepackage{textcomp} 
%\usepackage{array}
%\usepackage{varwidth}
%\usepackage[american]{babel}
%usepackage{mathtools} % fixes and extends amsmath
%mathtoolsset{mathic}
%\allowdisplaybreaks
%\usepackage{mathptmx}
%\usepackage{tabu}
%%\usepackage{breqn}
%\usepackage{algorithm,algorithmic,bm}
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%% Suggested packages, as needed:
%\usepackage{booktabs} % commands to create good-looking tables
%\usepackage{tikz} % nice language for creating drawings and diagrams - required for 
%drawing custom shapes
%\usetikzlibrary{%
%	arrows,%
%	calc,%
%	fit,%
%	patterns,%
%	plotmarks,%
%	shapes.geometric,%
%	shapes.arrows,%
%	shapes.callouts,%
	% shapes.multipart,%
	% shapes.gates.logic.US,%
	% shapes.gates.logic.IEC,%
	% er,%
	% automata,%
%	topaths,%
%	trees,%
%	matrix,%
%	% calendar,%
%	folding,%
%	fadings,%
%	positioning,%
%	scopes,%
%	decorations.fractals,%
%	decorations.shapes,%
%	decorations.text,%
%	decorations.pathmorphing,%
%	decorations.pathreplacing,%
%	decorations.footprints,%
%	decorations.markings,%
%	shadows}
%\usepackage{trace-pgfkeys}
\begin{document}
\title{Approximating Information-Theoretic Scores\\for Computer Adaptive Tests\\in Bayesian and Credal Networks}
%%\thanks{Supported by organization x.}}
%\titlerunning{Abbreviated paper title}
\author{Alessandro Antonucci \and
Francesca Mangili \and\\
Claudio Bonesana \and
Giorgia Adorni}
%\authorrunning{F. Author et al.}
\institute{Istituto Dalle Molle di Studi sull'Intelligenza Artificiale, Lugano, Switzerland\\
\email{\{alessandro,francesca,claudio.bonesana,giorgia.adorni\}@idsia.ch}}
\maketitle
\begin{abstract}
A test is adaptive when the sequence and the number of questions is tuned on the basis of the estimated skills of the test taker. Graphical models such as Bayesian networks allow to model the uncertainty about the questions and the skills in an highly interpretable fashion, especially when coping with multiple skills. Yet, the quantification of the uncertainty in the question/skill relations can be better quantified by interval-valued probabilistic values in the model. This might make inference considerably harder in the underlying model, this being especially the case for the information theoretic quantities generally used as a score to drive the adaptation process.
Here we present an alternative score based on the mode of the posterior probabilities of the model. We show how this makes considerably simpler the evaluation of the score in the credal case. Numerical tests are promising, we show how the performance are similar in the Bayesian network case, while xxx.
%considered. 
%We propose an alternative 
%We present.
%with xxx. Interval valued quantification
%We suggest the use of credal networks, a generalization of Bayesian networks based on sets of probability mass functions, to implement adaptive tests exploiting the knowledge of the test developer instead of training on databases of answers. Compared to Bayesian networks, these models might offer higher expressiveness and hence a more reliable modeling of the qualitative expert knowledge. The counterpart is a less straightforward identification of the 
%information-theoretic measure controlling the question-selection and the test-stopping criteria. We elaborate on these issues and propose a sound and computationally feasible procedure. Validation against a Bayesian-network approach on a benchmark about German language proficiency assessments suggests that credal networks can be reliable in assessing the student level and  effective in reducing the number of questions required to do it.
%150-200 words - 12 pages
\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}

\section{Testing Algorithms}
The typical goal of a test or exam is to evaluate the knowledge level of a student or examinee $\sigma$ on the basis of her answers to a number of questions or exercises. Let $\bm{Q}$ denote a repository of questions available to the instructor. The order and the number of questions from $\bm{Q}$ asked to $\sigma$ might not be fixed. We call \emph{testing algorithm} (TA) a procedure taking care of the selection of the sequence of questions asked to the student and able to decide when the test should stop. A standard TA pseudocode is in Algorithm \ref{alg:ta}, where $\bm{e}$ denotes the array of the answers collected from the student $\sigma$.

\begin{algorithm}[H]
    \SetAlgoLined
    \KwResult{Write here the result }
    initialization\;
    \While{While condition}{
        instructions\;
        \eIf{condition}{
            instructions1\;
            instructions2\;
        }{
            instructions3\;
        }
    }
    \caption{How to write algorithms}
\end{algorithm}

\begin{algorithm}[htp]
    \begin{algorithmic}[1]
    \STATE $\bm{e}=\emptyset$
        \WHILE{ {\bf not} $\tt{Stopping}(\bm{e})$}
        \STATE $Q^* \gets \tt{PickQuestion}(\bm{Q},\bm{e})$
        \STATE $q^* \gets {\tt{Answer}}(Q^*,\sigma)$
        \STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
        \STATE $\bm{Q} \gets \bm{Q} \setminus \{ Q^*\}$
        \ENDWHILE
        \STATE {\bf return} $\tt{Evaluate}(\bm{e})$
    \end{algorithmic}\label{alg:ta}
\caption{Testing algorithm. Student profile $\sigma$ and question repository $\bm{Q}$ are inputs.}
\end{algorithm}

@@

%	\begin{algorithm}[htp!]
%		\caption{Single skill, precise model\\
%			a model (BN, skeleton) $M$ over the skills only
%			\\a dataset of $n$ students $\{s^i\}_{i=1}^n$,\\a dataset of $m$ questions 
%			$\mathcal{Q}:=\{Q^j\}_{j=1}^m$,\\
%			the CPTs of the questions in $\mathcal{Q}$, i.e., $\{P(Q^j|S)\}_{j=1}^m$\\
%			the student answer models $\{\tilde{P}(Q^j|S)\}$\\
%			an entropy threshold $h^*$,\\
%			a score function for questions $\gamma$
%			\label{alg:simple}}
%		\begin{algorithmic}[1]
%			\FOR {$i\gets\{1,\ldots,n\}$}
%			\STATE $(M',\mathcal{Q}',\mathcal{Q}'',\bm{e}) \gets 
%			(M,\mathcal{Q},\emptyset,\emptyset)$
%			\WHILE{ $h > h^* \mathrm{\bf and}\, \mathcal{Q}' \neq \mathcal{Q}$}
%			\STATE $Q^* \gets \arg\max_{Q \in \mathcal{Q}'}\gamma(M',Q,\bm{e})$
%			\STATE{$\mathcal{Q}'\gets \mathcal{Q}' \setminus \{ Q^*\}$}
%			\STATE{$\mathcal{Q}''\gets \mathcal{Q}'' \cup \{ Q^*\}$}
%			\STATE{$q^* \gets \mathrm{sampling} \sim \tilde{P}(Q^*|s^i)$}
%			\STATE $M' \gets \mathrm{addChild}(M',Q,S,P(Q|S))$
%			\STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
%			\STATE $h \gets H[P_{M'}(S|\bm{e})]$
%			\ENDWHILE
%			\STATE $\sigma_i \gets \arg\max_{s\in\mathcal{S}} P_{M'}(s|\bm{e})$
%			\ENDFOR
%			\STATE {\bf return} $(\sigma_1,\ldots,\sigma_n)$
%		\end{algorithmic}
%	\end{algorithm}
	Three possible scores:
	\begin{eqnarray}
		\gamma(Q,\bm{e}) := -H[S|Q,\bm{e}] = -\sum_q P(q) \cdot H[S|\bm{e},q]&&\\
		\gamma'(Q,\bm{e}) :=  -\sum_q P(q) \cdot \max_{s\in\mathcal{S}}  P[s|\bm{e},q]&&\\
		\gamma''(Q,\bm{e}) :=  |P(Q=1|\bm{e})-0.5|&&
	\end{eqnarray}

@@

%	\begin{algorithm}[htp!]
%		\caption{Single skill, credal model\\a dataset of $n$ students $\{s^i\}_{i=1}^n$,\\a 
%		dataset of $m$ questions $\mathcal{Q}:=\{Q^j\}_{j=1}^m$,\\
%			the credal CPTs of the questions in $\mathcal{Q}$, i.e., 
%			$\{\overline{P}(Q^j|S)\}_{j=1}^m$\\
%			an upper entropy threshold $\overline{h}^*$,\\
%			a score function for questions $\sigma$
%			\label{alg:simple2}}
%		\begin{algorithmic}[1]
%			\FOR {$i\gets\{1,\ldots,n\}$}
%			\STATE $(\mathcal{Q}',\mathcal{Q}'',\bm{e}) \gets 
%			(\mathcal{Q},\emptyset,\emptyset)$
%			\WHILE{ $h > h^* \mathrm{\bf and}\, \mathcal{Q}' \neq \mathcal{Q}$}
%			\STATE $Q^* \gets \arg\max_{Q \in \mathcal{Q}'}\gamma(Q,\bm{e})$
%			\STATE{$\mathcal{Q}'\gets \mathcal{Q}' \setminus \{ Q^*\}$}
%			\STATE{$\mathcal{Q}''\gets \mathcal{Q}'' \cup \{ Q^*\}$}
%			\STATE{$q^* \gets \mathrm{sampling} \sim P(Q^*|s^i)$}
%			\STATE $\mathrm{addChild}(Q,S,P(Q|S))$
%			\STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
%			\STATE $h \gets H[P(S|\bm{e})]$
%			\ENDWHILE
%			\STATE $\sigma_i \gets \arg\max_{s\in\mathcal{S}} P(s|\bm{e})$
%			\ENDFOR
%			\STATE {\bf return} $(\sigma_1,\ldots,\sigma_n)$
%		\end{algorithmic}
%	\end{algorithm}
	Three possible scores:
	\begin{eqnarray}
		\gamma(Q,\bm{e}) := -H[S|Q,\bm{e}] = -\sum_q P(q) \cdot H[S|\bm{e},q]&&\\
		\gamma'(Q,\bm{e}) :=  -\sum_q P(q) \cdot \max_{s\in\mathcal{S}}  P[s|\bm{e},q]&&\\
		\gamma''(Q,\bm{e}) :=  |P(Q=1|\bm{e})-0.5|&&
	\end{eqnarray}

%	\begin{algorithm}[htp!]
%		\caption{Given a dataset of student profiles $\bm{S}$\label{alg:simple3}}
%		\begin{algorithmic}[1]
%			\FOR {$s\in\bm{S}$}
%			\WHILE{ $h > h^*$}
%			\STATE $Q^* \gets \mathrm{FindBestQuestion}(\bm{Q}$)
%			\STATE $q^* \gets \mathrm{SimulateAnswer}(\sigma)$
%			\STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
%			\STATE $h \gets H[P(S|\bm{e}]$
%			\ENDWHILE
%			\ENDFOR
%			\STATE {\bf return} $\arg\max P(s|\bm{e})$
%		\end{algorithmic}
%	\end{algorithm}

@@

	\subsection*{Toy Example}
	Consider a Boolean skill $S$ with states $s_0$ and $s_1$ and a Boolean 
	question/answer $Q$. Let us shape the model as a BN, $S\to Q$. The prior $P(S)$ is 
	specified by a parameter $p:=P(s_1)$. The question CPT $P(Q|S)$ might be specified 
	instead by two parameters $\pi_1:=P(q_1|s_1)$ and $\pi_0:=P(q_1|s_0)$. The 
	informativeness score we assign two the question is
	\begin{equation}
		\sigma_Q = H[S|Q]:=H[S|q_0]P(q_0)+H[S|q_1]P(q_1)\,.
	\end{equation}
	We have
	\begin{equation}
		P(q_1)=\pi_1 p + \pi_0 (1-p)
	\end{equation}
	while $P(q_0)=1-P(q_1)$ and also
	\begin{equation}
		P(s_1|q_1)=\frac{\pi_1 p}{\pi_1 p + \pi_0 (1-p)}=\frac{1}{1+\frac{\pi_0(1-p)}{\pi_1 p}}
	\end{equation}
	and
	\begin{equation}
		P(s_1|q_0)=\frac{p (1-\pi_1)}{p(1-\pi_1) +  (1-p)(1-\pi_0)} = \frac{1}{1+ \frac{ 
		(1-p)(1-\pi_0)}{p (1-\pi_1)}} 
	\end{equation}
	while $P(S=0|Q=1)$ by normalization. Accordingly:
%	\begin{multline}
%		\sigma_Q(p,\pi_0,\pi_1)=\\
%		h \circ f[\gamma/l(p)] \cdot t +
%		h \circ f[\gamma'/l(p)] \cdot (1-t)\,
%		%\theta(\frac{\pi_0(1-p)}{\pi_1 p}) [\pi_1 p + \pi_0 (1-p)]\\
%		%+ \theta(\frac{ (1-p)(1-\pi_0)}{p (1-\pi_1)}) [1-\pi_1 p + \pi_0 (1-p)]
%	\end{multline}
	where $\gamma = \frac{\pi_0}{\pi_1}$, $\gamma' = \frac{1-\pi_0}{1-\pi_1}$, and $t = \pi_1 
	p + \pi_0 (1-p)$.

@@

%	\begin{multline}
%		\sigma_Q(p,\pi_0,\pi_1)=\\
%		m\bigl(\frac{\pi_1 p}{P(q_1)}\bigr) \cdot P(q_1)  +
%		m\bigl(\frac{(1-\pi_1) p}{1-P(q_1)}\bigr) \cdot (1-P(q_1))\,
%	\end{multline}

	But, as $P(q_1)\geq 0$, then
%	\begin{multline}
%		m\bigl(\frac{\pi_1 p}{P(q_1)}\bigr) =\\
%		2max\bigl(\frac{\pi_1 p}{P(q_1)},1-\frac{\pi_1 p}{P(q_1)} \bigr) =\\
%		2max\bigl(\frac{\pi_1 p}{P(q_1)},\frac{\pi_0(1- p)}{P(q_1)} \bigr) =\\
%		\frac{2}{P(q_1)}max\bigl(\pi_1 p,\pi_0(1- p)\bigr).\\
%	\end{multline}

	Similarly, as $1-P(q_1)\geq 0$, 
%	\begin{multline}
%		m\bigl(\frac{(1-\pi_1) p}{1-P(q_1)}\bigr) =\\
%		\frac{2}{1-P(q_1)}max\bigl((1-\pi_1) p,(1-\pi_0)(1- p)\bigr),\\
%	\end{multline}

@@

%	\begin{multline}
%		\sigma_Q(p,\pi_0,\pi_1)= \\
%		2 max\{\pi_1 p, \pi_0 (1-p)\}+
%		2 max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\}\,
%	\end{multline}

@@

	However I think we can split the optimization into 4 quadratic optimizations.
	Let's use the following parametrization:
%	\begin{multline}\label{eq:minimization}
%		\min_{p,\pi_0,\pi_1} \sigma_Q(p,\pi_0,\pi_1) = \\
%		2\min_{p,\pi_0,\pi_1} \bigl( \max\{\pi_1 p, \pi_0 (1-p)\} + \\
%		~~~ \max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\} \bigr) \approx \\
%		2 \bigl( \min_{p,\pi_0,\pi_1}  \max\{\pi_1 p, \pi_0 (1-p)\} + \\
%		~~~ \min_{p,\pi_0,\pi_1} \max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\} \bigr) 
%	\end{multline}

@@

%	\begin{multline}
%		\tilde{P}(s=0,q) = \min_{\pi_1 ,p} \pi_1 p \\
%		\begin{array}{ll}
%			\text{subject to} & \pi_1 p > \pi_0 (1-p) \\
%			~&\underline{x} \leq x\leq \overline{x}\\ 
%		\end{array}
%	\end{multline}
	and 
%	\begin{multline}
%		\tilde{P}(s=1,q) = \min_{\pi_0 ,p} \pi_0 (1-p) \\
%		\begin{array}{ll}
%			\text{subject to} & \pi_1 p < \pi_0 (1-p)\\
%			~&\underline{x} \leq x\leq \overline{x}\\ 
%		\end{array}
%	\end{multline}

@@

%	\begin{multline}
%		\tilde{P}_1 = \min_{\pi_0,\pi_1,p} \pi_1 p+ (1-\pi_1)p = p \\
%		\begin{array}{ll}
%			\text{subject to} & \pi_1 p > \pi_0 (1-p) \\
%			~&  (1-\pi_1)p > (1-\pi_0)(1-p)  \\
%			~&\underline{x} \leq x\leq \overline{x}\\ 
%		\end{array}
%	\end{multline}
	and so on. However, in this case, the number of optimizations to solve should be 
	$N_s^{N_q}$, that is, it grows exponentially with  $N_q$.

	\paragraph{*** Alessandro's reformulation ***}
%	\begin{equation}
%		\begin{split}
%			\text{min} \displaystyle \, \pi_1 \cdot p \\
%			\text{subject to} & \displaystyle \pi_1 p > \pi_0 (1-p)\\
%			&\displaystyle \underline{\pi}_0 \leq \pi_0 \leq \overline{\pi}_0 \\
%			&\displaystyle \underline{\pi}_1 \leq \pi_1 \leq \overline{\pi}_1 \\
%%		\end{split}
%	\end{equation}
	with the new variable specification:
	\begin{eqnarray}
		x_1&:=&\pi_1 \cdot p \,,\\
		x_2&:=&\pi_0 \cdot p \,,\\
		x_3&:=&(1-\pi_1) \cdot p \,,\\
		x_4&:=& \pi_0 \cdot (1-p)\,.\\
	\end{eqnarray}
	the problem becomes:
%	\begin{equation}
%		\begin{split}
%			\text{min} \displaystyle \, x_1 \\
%			\text{subject to\phantom{xx}} & \displaystyle x_1 > x_4\\
%			&\displaystyle \underline{\pi}_0 \leq x_2+x_3 \leq \overline{\pi}_0 \\
%			&\displaystyle \underline{\pi}_1 \leq x_1+x_4 \leq \overline{\pi}_1 \\
%			&\displaystyle \underline{p} \leq x_1+x_3 \leq \overline{p} \\
%		\end{split}
%	\end{equation}
